Turbulence in compact to giant HII regions

### 2021-07-30 mnras_template.tex
Javier vacation changes up to 2021 July 30

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
  We apply the technique to archival observations of a diverse sample of 8 \hii{} regions
  in the Milky Way and other Local Group galaxies,
  which span more than two orders of magnitude in size and luminosity.
  By fitting a simple functional form to the second-order velocity structure function,
  we extract three parameters for the fluctuations in each region:
  total velocity dispersion, \(\sigma\),
  autocorrelation length, \(r_0\), and power-law slope, \(m\).
  The velocity dispersion is found to correlate primarily with luminosity,
  while the autocorrelation length correlates primarily with the size of the region.
  The power-law slope shows an apparent correlation with distance,
  but this is probably an artifact of poor spatial resolution for the most distant regions.
  \textbf{Add a sentence about the conclusions!}
  % We study the turbulent velocity fluctuations in the ionized gas of four giant HII regions using the radial velocity field in the H$\alpha$ emission line. The data was acquired by long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope. Each velocity sample is statistically analyzed with the second order structure function. The correlations in our results shows evidence that the velocity field can be consider in a turbulent state. This turbulent motions are described by a power-law with a mean index of 1.7 for different sized regions at different distances. The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
\end{abstract}

@@

The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that builds the idea of a turbulent interstellar medium. Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field, evidence of random motions. The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes. Also, It is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence. Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources an their relation to turbulence still is unclear.

@@

The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second order structure function (the Fourier transform of the energy spectrum, $E(k)$). This studies span from galactic HII regions like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.

@@

The non-thermal broadening on the spectral emission lines also has been suggested as evidence of disorder motions along the line-of-sight (LOS). \citet{smith1970} discovered that the line width of GEHRs was supersonic in the order of $\sigma \sim$ 17-26 km s\kms. \citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$). They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies. The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening. The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}. This features seems to drive visually the regions with filaments, arcs and shells. On their spectra double and multiple emission features are signature of these objects. \citet{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars. \citet{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.

@@

Using archival data we perform the second-order structure function on a sample of HII regions. Our sample spans in size from 4 pc to 400 pc and has luminosities between 10\(^{37}\) - 10\(^{39}\) erg s\(^{-1}\); from galactic to extragalactic HII regions. We apply an uniform methodology of a functional form of the structure function to characterize the turbulent using the  autocorrelation length, \(r_0\), and power-law slope, \(m\). Our results are compared with physical properties of each region, which reveal correlations between them, and are also compared with previous investigations. With this work we aim to fill a gap in statistical analysis of turbulence between galactic and giant HII regions.

@@

@@

We used previous published observational data to measure the second-order velocity structure function for a number of compact and lower luminosity regions.

We use data from \citet{1987A&A...176..347H} of the Orion Nebula (M42) located at 440 pc \citep{2008AJ....136.1566O}. Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}. The main ionizing star is $\theta^{1}$Ori C (spectral type $\sim$O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster. The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.

Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively.

@@

\subsection{Regions in Local Group galaxies}

@@

\subsubsection{Giant extragalactic regions}

\paragraph{Observations}\label{sec:obs}

@@

NGC 595 is the second brightest giant HII region in the M33 galaxy with a length of 300 pc. The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}. \citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$. \citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.

@@

%It also shows some physical quantities of each region, among other parameters used in our analysis.

\begin{table*}
\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K}.}
\begin{tabular}{cccccccc}\hline
HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling  \\
Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor \\ \hline
NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7$\times$10$^{5}$ & 0.1 \\
NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  &  \\
Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02\\
Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    &\\
30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    &\\
Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 \\
NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     \\
Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012\\
Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027\\

\end{tabular}\label{tab:Reg}
\end{center}
\end{table*}

@@

One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density \citep{1984ApJ...277..556S}. They are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density. By means of describing their statistical properties, these fluctuations can be considered as a product of a stochastic  field.

The statistical tool we use is the second-order structure function, $B(r)$, defined as:

@@

where, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{r}$) is the number of points at each separation, called lag.

As a justification for the use of the structure function, we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size. This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.

For our fit we use the functional form of the structure function:

\begin{equation}\label{eq:b}
b(r)=2[1-C(r)]\zeta
\end{equation}

where $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}. The term $r_{0}$ is the correlation length of the turbulence and $m$ is the index that adjust our results. The term $\zeta$ is a correction for small scales considering a seeing, $s_{0}$, an has the form $tanh^{2}[(r/2s_{0})^2]$.

@@

The Table \ref{tab:Data} shows the statistical properties of each individual sample. The mean, \(\mu\), and the variance, \(\sigma^{2}\), along the number of points of each sample. The last column shows previous publications where the data was used. In appendix \ref{sec:VelMaps} we show in the Figure \ref{fig:hist} the histograms of the velocity samples of each HII region where we applied equation \ref{eq:S}. The Figures \ref{fig:M604}-\ref{fig:MOrion} show the two-dimensional radial velocity map of each region.

\begin{table}
  \begin{center}
    \caption{General statistical properties of the centroid velocities.
      a) \citet{tanco1997}
      b) \citet{2019arXiv191203543M}
      c) \citet{Castro:2018a}
      d) \citet{Damiani:2016a}
      e) \citet{Damiani:2017b}
      f) \citet{1987A&A...176..338H}
      g) \citet{1987A&A...176..347H}.
    } 
\begin{tabular}{cccccc}\hline
HII    &  $\mu$   & $\sigma^{2}$        &  No. of  &\(s_0\)& Previously  \\
   Region       &  [km/s]  &  [km$^{2}$/s$^{2}$] &  points   &[pc]& used in:\\\hline
NGC 604   &  3.56    &    54.63            &    9 510    &1.73&  a,b     \\
NGC 595   &  2.82    &    44.13            &    8 765    &1.73&  -     \\
Hubble V  & -1.23    &    7.87             &    5 832    &1.02&   -    \\
Hubble X  & -5.95    &    12.9             &    6 925    &1.02&  -     \\
30Dor     & 265.56*  &    252.79           &    363 059    &0.08&   c    \\
Carina    & -8.83    &    17.89         &   855    &&   d    \\
NGC 346   &          &       31.36           &    112 796   &&       \\
Lagoon    & 3.21 / -6.26 &     8.95 / 7.53    &    566 / 1 176    &&  f / e   \\
Orion     &     -1.25    &     10.43    &    359    &&    g   \\
\end{tabular}\label{tab:Data}
\end{center}
\end{table}

@@

Table \ref{tab:Res} presents the main parameters we obtain from the analysis on the fluctuations of the velocities. The first column is the velocity dispersion, \(\sigma\), of each sample of centroid velocities. The second column is the correlation length, \(r_0\). The third column is the index \(m\) that is used to fit our results. This index is used as a reference for comparison between theory and observations. In the forth column we show the separation where the value 2\(\sigma\) is reached. We also show the ratio \(r_{max}/r_{0}\), where \(r_{max}\) is the maximum separation or lag in pc; this value is related to the size of each sample box. With the aim to investigate how statistically homogeneous the regions are, we also show the value of $\sigma_{LOS}$. In the appendix \ref{sec:StructFunct} the Figures \ref{fig:SF604}-\ref{fig:SFM42} show the second-order structure functions of the different HII regions for the \halpha\ emission line.

The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc. For NGC 604 the index is 1.7 with a correlation length of 9 pc. The structure functions keep going up to scales of 70 pc following a periodic pattern. In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}. Figure \ref{fig:SF604} shows that the structure functions for NGC 604, follow a periodic behavior around 2$\sigma$. We can think of a wave starting around 30 pc, with a series of $ >$2$\sigma$ values up to $\sim$100 pc. Then $<$2$\sigma$ values follow until the scales of 150 pc. Therefore we relate periodic behavior to scales of magnitude $\sim$100 pc across our sample box. For NGC 595 the values obtained are 1.55 and 8.8. The structure function goes up until 30 pc, reaching values above 2$\sigma$ before falling.

For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.5 and 1.4, with a correlation length of 3.5 and 2.7 pc, respectively. Both regions reach a maximum of 2$\sigma$ around 20 pc. The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and and index of 1.22.

The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}. Also, it is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}; for this sample we show our results. Carina has an index of 1 with a correlation length of 0.55 pc. The structure function shows large-scale oscillatory pattern, with peaks at \(\sim\) 3, 6 and 10 pc. The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.5 pc and a index of 1.15. For this region the structure function reach a constant value of 12 km$^{2}$/s$^{2}$ from 2 to 6 pc. For scales greater than 6 pc large-scale correlation is found up to 15 pc. M42 results shows an index of 0.75 with a correlation length of 0.65.

@@

@@

\clearpage

>>>>

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
  We apply the technique to archival \halpha\ observations of a diverse sample of 8 \hii{} regions
  in the Milky Way and other Local Group galaxies,
  which span more than two orders of magnitude in size and luminosity.
  By fitting a simple functional form to the second-order velocity structure function,
  we extract three parameters for the fluctuations in each region:
  total velocity dispersion, \(\sigma\),
  autocorrelation length, \(r_0\), and power-law slope, \(m\).
  The velocity dispersion is found to correlate primarily with luminosity,
  while the autocorrelation length correlates primarily with the size of the region.
  The power-law slope shows an apparent correlation with distance,
  but this is probably an artifact of poor spatial resolution for the most distant regions.
  \textbf{Add a sentence about the conclusions!}
  % We study the turbulent velocity fluctuations in the ionized gas of four giant HII regions using the radial velocity field in the H$\alpha$ emission line. The data was acquired by long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope. Each velocity sample is statistically analyzed with the second order structure function. The correlations in our results shows evidence that the velocity field can be consider in a turbulent state. This turbulent motions are described by a power-law with a mean index of 1.7 for different sized regions at different distances. The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
\end{abstract}

@@

It is known that the speed of sound in a HII region is of the order of \(c_{HII} \sim\) 13 km s\kms.
\citet{smith1970} discovered that the probable velocities of internal motions of extragalactic HII regions, \(\sigma_{W}\) (line width integrated over the whole HII region), were in the range of $\sim$ 19-34 km s\kms\ covering supersonic values.
\citet{skillman1984kinematics} found broad profiles in giant extragalactic HII regions (GEHRs) that have a FWHM\(>\)30km s\kms. 
This property is mainly used to distinguish between 'normal' and 'giant' HII regions. Other differences are their size, luminosity and their stellar population. 
For the velocity to be supersonic it is necessary a continuous mechanism to maintain the observed motions, as supersonic motions are expected to dissipate energy via shocks \citep{1994Ap&SS.216..285C}. 
Also, this non-thermal broadening on the spectral emission lines has been suggested as evidence of disorder motions along the line-of-sight (LOS) of the ionized gas. 
Turbulence is suggested as a mechanism that can stir the medium and maintain the supersonic velocities.

The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that supports the idea of a turbulent interstellar medium.
Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.
The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
Also, it is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources and their relation to turbulence still is unclear.

\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $L_{H} \sim \sigma ^{\sim 4}$).
They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(L_{H_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass finding \(\sigma \propto r^{0.42}\), \(L_{H_{\alpha}} \propto r^{2.72}\) and \(L_{H_{\alpha}} \propto \sigma^{4.18}\). This results imply that the same process are seen at high redshifts and the current epoch in star forming regions. \citet{2015MNRAS.449.3568M} found that the relation is also found in dwarf galaxies with a \(L_{H_{\alpha}} \propto \sigma^{5}\).

The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening.
The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}.
This features seems to drive visually the regions with filaments, arcs and shells.
On their spectra double and multiple emission features are signature of these objects.
\citet{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars.
\citet{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.

@@

The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second order structure function (the Fourier transform of the energy spectrum, $E(k)$).
This studies span from galactic HII regions \citep{1986ApJ...300..624R} like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.

@@

@@

Using archival data we perform the second-order structure function on a sample of HII regions.
Our sample spans in size from 4 pc to 400 pc and has luminosities between 10\(^{37}\) - 10\(^{39}\) erg s\(^{-1}\); from galactic to extragalactic HII regions.
We apply an uniform methodology of a functional form of the structure function to characterize the turbulent using the  autocorrelation length, \(r_0\), and power-law slope, \(m\).
Our results are compared with physical properties of each region and are also compared with previous investigations.
With this work we aim to fill a gap with an uniform statistical analysis of turbulence between galactic and giant HII regions.

The paper follows the next order...
Section 2...

@@

We used previous published observational data to measure the second-order velocity structure function for a number of compact and lower luminosity regions. Table \ref{tab:Reg} shows the HII regions names
with physical properties of each region.

@@

We use data from \citet{1987A&A...176..347H} of the Orion Nebula (M42) located at 440 pc \citep{2008AJ....136.1566O}.
Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}.
The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster.
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.

A 106 cm-Cassegrain telescope at Observatorium Hoher List was used with a Fabry-Pérot interferometer having the étalon a separation of 0.5 mm. 
Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
The exposures are overlapped and fall into one square of a grid with a width of 1' sentered at \(\theta^{1}\)Ori C \citep{1987A&A...176..347H}.

@@

Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
The ESO VLT/FLAMES multi-fiber spectograph was used for observations (Gaia-ESO Survey internal release \(iDR4\)) of Lagoon nebula  and Carina nebula \citep{2002Msngr.110....1P}. 
Mainly the spectra were obtained with the Giraffe HR15N setup (\(R \sim19 000\), wavelength range 6444-6818 A) which allow to observe \halpha\ emission line. 
The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.

@@

NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very LArge Telescope (VLT). 
Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed. 
The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalogue of \citet{1999A&A...341...98S}. 
The final spectra span 495-9366 A, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.

\begin{table*}
\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}}
\begin{tabular}{ccccccccc}\hline
HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling & \(\sigma_{W}\) \\
Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor & [km/s] \\ \hline
NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7 $\times$ 10$^{5}$ & 0.1 & 23.1 \\
NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  & 4.6 $\times$ 10$^{5}$ & & 27.1 \\
Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02 & 13.4 \\
Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    & & 14.7 \\
30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    & & 31.7 \\
Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 & \\
NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     & \\
Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012 & \\
Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\
\end{tabular}\label{tab:Reg}
\end{center}
\end{table*}

\subsection{Regions in M33 galaxy and NGC 6822}

@@

NGC 595 is the second brightest giant HII region in the M33 galaxy.
The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
\citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
\citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.

@@

@@

One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density \citep{1984ApJ...277..556S}.
They are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
By means of describing the statistical properties of these fluctuations they can be assumed as a product of a stochastic field statistical tools.

The statistical function we use to study the velocity field of the HII regions is the second-order structure function, $B(r)$, defined as:

@@

where, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{r}$) is the number of points at each separation \(r\), called lag.

As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.

We also use the functional form of the structure function:

\begin{equation}\label{eq:b}
b(r)=2[1-C(r)]\zeta+\eta
\end{equation}

where $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:S} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
The term $\zeta$ is a correction for small scales considering a Gaussian seeing, $s_{0}$, and has the form $tanh^{2}[(r/2s_{0})^2]$, and \(\eta\) is the observational noise.

The results and the errors of $r_{0}$ and $m$ are obtained using equations \ref{eq:S} and \ref{eq:b} in a chi-square (\(\chi^2)\) statistic in order to do a non-linear least-squares fit of a model to our data. 
In this way we avoid one fundamental problem in the interpretation of the structure function results. The slope in the majority of previous studies and hence, the correlation length, is obtained by eye. 
The canonical way to find it is to determine a particular range of ascending values in the structure function results. 
If this increase in values is reversed it is commonly assumed that one particular range has been found. 
In some cases this procedure keeps going up to large scales, having two or more inertial regimes giving as a interpretation multiple energy injection scales.
Since the results using the canonical method aren't conclusive we choose the chi-square (\(\chi^2)\) statistic to present the significance of our results.
This way we can maintain consistency in our analysis of multiple regions and keep the possibility open to enhance our sample with future consistency.

@@

The Table \ref{tab:Data} shows the statistical properties of each individual sample.
The mean, \(\mu\), and the variance, \(\sigma^{2}\), along the number of points of each sample.
The last column shows previous publications where the data was used. For the first 4 regions in Table \ref{tab:Data} the value of \(\mu\) is the observed radial velocity accounting for heliocentric correction and subtracting the corrected radial velocity value of the most luminous pixel.

%In appendix \ref{sec:VelMaps} we show in the Figure \ref{fig:hist} the histograms of the velocity samples of each HII region where we applied equation \ref{eq:S}.
%The Figures \ref{fig:M604}-\ref{fig:MOrion} show the two-dimensional radial velocity map of each region.

\begin{table*}
  \begin{center}
    \caption{General statistical properties of the centroid velocities.
      a) \citet{tanco1997}
      b) \citet{2019arXiv191203543M}
      c) \citet{Castro:2018a}
      d) \citet{Damiani:2016a}
      e) \citet{Damiani:2017b}
      f) \citet{1987A&A...176..347H}
      g) \citet{arthur2016turbulence}.
    } 
\begin{tabular}{cccccc}\hline
HII    &  $\mu$   & $\sigma^{2}$        &  No. of  &\(s_0\)& Previously  \\
   Region       &  [km/s]  &  [km$^{2}$/s$^{2}$] &  points   &[pc]& used in:\\\hline
NGC 604   &  3.56    &    54.63            &    9 510    &1.73&  a,b     \\
NGC 595   &  2.82    &    44.13            &    8 765    &1.73&  -     \\
Hubble V  & -1.23    &    7.87             &    5 832    &1.02&   -    \\
Hubble X  & -5.95    &    12.9             &    6 925    &1.02&  -     \\
30Dor     & 265.56*  &    252.79           &    363 059    &0.2&   c    \\
Carina    & -8.83    &    17.89         &   855    &&   d    \\
NGC 346   &          &       31.36           &    112 796   &&       \\
Lagoon    & -6.26 &    7.53    &    1 176    &&   e   \\
Orion Large     &     -1.25    &     10.43    &    359    &&    f   \\
Orion Small     &         &        &        &&    g   \\
\end{tabular}\label{tab:Data}
\end{center}
\end{table*}

@@

Table \ref{tab:Res} presents the main parameters we obtain from the analysis on the fluctuations of the velocities.
The first column is the velocity dispersion, \(\sigma\), of each sample of centroid velocities.
The second column is the correlation length, \(r_0\).
The third column is the index \(m\) that is used to fit our results.
This index is used as a reference for comparison between theory and observations.
In the forth column we show the separation where the value 2\(\sigma\) is reached.
We also show the ratio \(r_{max}/r_{0}\), where \(r_{max}\) is the maximum separation or lag in pc; this value is related to the size of each sample box.
With the aim to investigate how statistically homogeneous the regions are, we also show the value of $\sigma_{LOS}$.

The final column shows the Taylor scale, \(l_T\), which measures the average spatial extent of velocity gradients. \citet{1999ApJ...524..895M} define this scale as \citet{1987A&A...176..347H}

\begin{equation}\label{eq:TS}
l_T=\dfrac{\sigma r_s}{\sigma_{r_s}}
\end{equation}

where \(r_s\) is the smallest separation \(r\) and \(\sigma_{r_s}\) the value of the structure function at that separation. It is possible to calculate how this Taylor micro-scale is related to the correlation length by:

\begin{equation}\label{eq:TS1}
l_T=\dfrac{r_s}{\sqrt{2}}(\dfrac{r_0}{r_s})^{m/2}
\end{equation}

%In the appendix \ref{sec:StructFunct} the Figures \ref{fig:SF604}-\ref{fig:SFM42} show the second-order structure functions of the different HII regions for the \halpha\ emission line.
The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
For NGC 604 the index is correspond to 1.95 with a correlation length of 8.75 pc.
The structure functions keep going up to scales of 70 pc following a periodic pattern.
In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
The structure functions for NGC 604, follow a periodic behavior around 2$\sigma$.
We can think of a wave starting around 30 pc, with a series of $ >$2$\sigma$ values up to $\sim$100 pc.
Then $<$2$\sigma$ values follow until the scales of 150 pc.
Therefore we relate periodic behavior to scales of magnitude $\sim$100 pc across our sample box.
For NGC 595 the values obtained are 1.75 and 9 pc.
The structure function goes up until 30 pc, reaching values above 2$\sigma$ before falling.

For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.7 and 1.62, with a correlation length of 3.62 and 2.7 pc, respectively.
Both regions reach a maximum of 2$\sigma$ around 20 pc.
The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and and index of 1.22.
NGC 346 has a correlation length of 1.4 and an index of 1.13.

The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}.
Also, it is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}; for this sample we show our results.
Carina has an index of 1 with a correlation length of 0.55 pc.
The structure function shows large-scale oscillatory pattern, with peaks at \(\sim\) 3, 6 and 10 pc.

The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.378 pc and a index of 1.13.
For this region the structure function reach a constant value of 12 km$^{2}$/s$^{2}$ from 2 to 6 pc.
For scales greater than 6 pc large-scale correlation is found up to 15 pc.

For Orion (M42) we have the opportunity to study two different observations with different implications. \citet{1987A&A...176..347H} observations allow us to study the large scale of the nebula, covering 4 pc, while \cite{arthur2016turbulence} allow us to study the small scales up to 0.4 pc. Large scales results shows an index of 0.84 with a correlation length of 0.9 pc while the small scales have 1.44 and 0.062 pc.

\begin{table*}
\begin{center}\caption{Main results.}
\begin{tabular}{cccccccccc}\hline
HII    &  \(\sigma\) &   \(r_0\) &    \(m\)   & r$_{2\sigma}$* &  \(r_{max}\)/\(r_0\)* & \(\sigma_{LOS}\)& \(l_T\)* & \(Re\)*& - \\
Region    &  [km/s] &  [pc]    &        & [pc] &      &[km/s]& [pc] & &  \\ \hline
NGC 604   &  7.39   &  8.75\(^{+0.68}_{-0.75}\)    &   1.95\(^{+0.12}_{-0.14}\)  & 27   & 14.7 & 7.69 &  5.1 & &  \\
NGC 595   &  6.64   &  8.99\(^{+0.58}_{-0.71}\)    &   1.75\(^{+0.10}_{-0.10}\) & 20   & 21.4 & 5.74 & 4.4  & &  \\
Hubble V  &  2.80   &  2.7\(^{+0.24}_{-0.14}\)   &   1.62\(^{+0.11}_{-0..09}\)  & 12   & 19.9 &      & 1.56 & &  \\ 
Hubble X  &  3.59   &  3.62\(^{+0.18}_{-0.15}\)    &   1.7\(^{+0.08}_{-0.09}\) & 15   & 22.1 &      & 1.95 & &  \\   
30 Dor    &  15.8    &   2.69\(^{+0.08}_{-0.03}\)    &   1.22\(^{+0.022}_{-0.007}\) & 11   & 8.9  &      & 0.69 & &  \\
Carina    &  4.22    &   0.55    &    1   & 2    & 16.1 & 2.7  &      & &  \\
NGC 346   &   5.6    &  1.4\(^{+0.05}_{-0.75}\)     &    1.13\(^{+0.03}_{-0.03}\) &     &     &     &  & &  \\
Lagoon    &  2.7     &   1.78\(^{+0.07}_{-0.07}\)     &   1.36\(^{+0.04}_{-0.03}\) &  6   & 10.1 &      &      & &  \\ 
Orion Large &  3.23    &   0.84\(^{+0.37}_{-0.24}\)    &   0.9\(^{+0.04}_{-0.04}\) &  -   & 27.6 &   6  &      & &  \\
Orion Small &   3.1 & 0.062\(^{+0.003}_{-0.001}\)      &  1.44\(^{+0.11}_{-0.01}\)  &     &  &  6   &      &  & \\

\end{tabular}\label{tab:Res}
\end{center}
\end{table*}

\subsection{Plane of sky radial velocity dispersion \(\sigma\)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%\clearpage
